### 2011-01-20 paper/problemDefinition.tex
working

>>>>

Given our physical robot, the gait learning problem aims to find a
\emph{gait} that maximizes some performance metric.  Gaits may loosely
be defined either with or without feedback from the robot.  Gaits
without feedback simply specify the motor commands to be given at any
time, and

\edit{Jason writing this now}

can best be
formulated as follows: find functions
